\documentclass[11pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}


  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}




\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother




\setcounter{secnumdepth}{0}




\title{Using Statistical Methods to Predict the Outcome of Basketball
Games  }



\author{\Large Sabrina
Ball\vspace{0.05in} \newline\normalsize\emph{}   \and \Large Joseph
Despres\vspace{0.05in} \newline\normalsize\emph{}  }


\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}





\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}


% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Sabrina Ball () and Joseph Despres ()},
             pdfkeywords = {},
            pdftitle={Using Statistical Methods to Predict the Outcome
of Basketball Games},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% Add an option for endnotes. -----


% add tightlist ----------
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% add some other packages ----------

% \usepackage{multicol}
% This should regulate where figures float
% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
\usepackage[section]{placeins}

% CSL environment change -----


\begin{document}

% \pagenumbering{arabic}% resets `page` counter to 1
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright
\maketitle  % title \par

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12}
\textbf{\authorfont Sabrina
Ball} \hskip 15pt \emph{\small }   \par \textbf{\authorfont Joseph
Despres} \hskip 15pt \emph{\small }   

}

}








\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small

\noindent Quick Summary


    \hbox{\vrule height .2pt width 39.14pc}


\end{abstract}


\vskip -8.5pt


 % removetitleabstract

\noindent 

\hypertarget{data}{%
\section{1. Data}\label{data}}

Our data comes from three different data sources Kaggle, NCAA, and a
March Madness bracket. First, a Kaggle\footnote{\url{https://www.kaggle.com/c/ncaam-march-mania-2021/data}}
machine learning challenge that has a comprehensive records of every US
division I basketball game played from 2003 to 2020. Second, the
NCAA\footnote{\url{http://stats.ncaa.org/rankings/change_sport_year_div}}
team statistics. Third, the tournament bracket in a nice .xls format we
obtained from a blog\footnote{\url{https://plexkits.com/march-madness-bracket/}}.

\hypertarget{variables}{%
\subsection{Variables}\label{variables}}

Our response is the outcome win/loss as a function of team statistics.
win \textbar{} Variable name \textbar{} Description \textbar{} Type
\textbar{} \textbar{} ------------------ \textbar{} -------------
\textbar{} ------- \textbar{} \textbar{} win \textbar{} \textbar{}
\textbar{} \textbar{} fg\_percent \textbar{} \textbar{} \textbar{}
\textbar{} opposingfg\_percent \textbar{} \textbar{} \textbar{}
\textbar{} ft\_percent \textbar{} \textbar{} \textbar{} \textbar{}
opposingft\_percent \textbar{} \textbar{} \textbar{} \textbar{} rpg
\textbar{} \textbar{} \textbar{} \textbar{} opposingrpg \textbar{}
\textbar{} \textbar{} \textbar{} st \textbar{} \textbar{} \textbar{}
\textbar{} opposingst \textbar{} \textbar{} \textbar{} \textbar{} to
\textbar{} \textbar{} \textbar{} \textbar{} opposingto \textbar{}
\textbar{} \textbar{} \textbar{} opposingbkpg \textbar{} \textbar{}
\textbar{} \textbar{} bkpg \textbar{} \textbar{} \textbar{}

\hypertarget{questions}{%
\section{2. Questions}\label{questions}}

Can we use statistical methods to predict outcomes of the March Madness
basketball games better than chance? Better than seed? Better than
betting markets?

\hypertarget{learning}{%
\section{3. Learning}\label{learning}}

We would like to learn how to make predictions with logistic regression.
We would like to come up with a good way to evaluate our predictions.
This will be dificult since the outcome is binary so we would need to
weight our predictions somehow and index our socres.

\hypertarget{methods}{%
\section{4. Methods}\label{methods}}

Logistic regression with a response prediction function.

\hypertarget{issues}{%
\section{5. Issues}\label{issues}}

The seeds are likely derrived from the predictors we are using.
Multicolinearity, will be something to watchout for because better teams
probally have better statistics.





\newpage
\singlespacing
\end{document}
