---
output: 
  stevetemplates::article:
    fig_caption: true
#bibliography: master.bib
urlcolor: blue
biblio-style: apsr
title: "Using Statistical Methods to Predict the Outcome of Basketball Games"
author:
- name: Sabrina Ball
  affiliation:
- name: Joseph Despres
  affiliation:
abstract: "Quick Summary"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
endnote: no
---

```{r eval=FALSE, include=FALSE}
op <- par(mar = rep(0, 4))
plot(imager::load.image("https://i.imgur.com/f0KNGaD.png"))
par(op)
```

```{r, include=FALSE}
# source(here::here("R", "explatoryAnalysis.R"))
```

# 1. Data
 ^[https://plexkits.com/march-madness-bracket/].

## Variables

Our response is the outcome win/loss as a function of team statistics. Win or loss coded 0 or 1. field goal precentage, 
win,fg_percent, opposingfg_percent, ft_percent, opposingft_percent, rpg, opposingrpg, st, opposingst, to, opposingto, opposingbkpg, bkpg

# 2. Questions

Can we use statistical methods to predict outcomes of the March Madness basketball games better than chance? Better than seed? Better than betting markets?

# 3. Learning

We would like to learn how to make predictions with logistic regression. We would like to come up with a good way to evaluate our predictions. This will be dificult since the outcome is binary so we would need to weight our predictions somehow and index our socres.

# 4. Methods

Logistic regression with a response prediction function.

# 5. Issues

The seeds are likely derrived from the predictors we are using. Multicolinearity, will be something to watchout for because better teams probally have better statistics.